Online resolving assembly graph by ONT long reads data

### 2019-06-14 paper.tex
d

\subsection*{Initial binning contigs into groups of abundances}
Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
This step is to cluster the significant nodes (longer than $10$Kbp) into different sets, namely significant abundance groups, based on their coverage values.

DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task.
The idea is to consider a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.

>>>>

\subsection*{Initial binning contigs into groups of abundances}
Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on their coverage values.

DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task.
The rationale is to approximate a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.
